---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# foofactors

<!-- badges: start -->
<!-- badges: end -->

The goal of **foofactors** is to provide simple helper functions for working with strings and factors.  
This package is created as part of an exercise following the *Whole Game* workflow from the book **R Packages (2nd edition)**.

Currently, the package provides one main function:

- `str_split_one()` — a safer, more convenient wrapper around `stringr::str_split()` that always returns a character vector instead of a list.

## Installation

You can install the development version of **foofactors** from GitHub with:

```r
# install.packages("devtools")
devtools::install_github("YOUR_GITHUB_USERNAME/foofactors")
```

## Usage

A common task when working with strings is splitting a single string into multiple pieces.  
Base R and stringr both return a list:

```{r}
(x <- "alfa,bravo,charlie,delta")

strsplit(x, split = ",")
stringr::str_split(x, pattern = ",")
```

`foofactors::str_split_one()` solves this by always returning a character vector:

```{r}
library(foofactors)

str_split_one(x, pattern = ",")
```

You can also use the `n` argument from stringr:

```{r}
str_split_one(x, pattern = ",", n = 2)
```

And you can use stringr’s pattern helpers:

```{r}
y <- "192.168.0.1"
str_split_one(y, pattern = stringr::fixed("."))
```
